---
title: "`r Master` Profile"
author: "Tom Hook"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  flexdashboard::flex_dashboard:
    theme:
      bg: "#FFFFFF"
      fg: "#000000"
      primary: "#FFFFFF"
      base_font:
        google: Open Sans
      code_font:
        google: JetBrains Mono
    orientation: columns
    vertical_layout: fill
params:
  Master:
    label: "Select a Master"
    value: ""
---

```{r, echo = FALSE}
# FILE:                   Games Table
# DESCRIPTION:            Creates a table of all the masters games that the users can filter on.

# AUTHOR:                 Tom Hook
# CONTACT:                thomashook1@outlook.com
# LAST UPDATED:           09/07/2023
# VERSION:                v0.2    
```

```{r setup, echo = FALSE, message = FALSE}
source("R Scripts/Snippets for Markdown/Setup.r")
```

Summary Page
=====

Column {data-width=600}
-----

### FIDE Rating over Time

```{r}
source("R Scripts/Snippets for Markdown/Elo Timeseries.r")

plotEloTimeseries
```

Column {.tabset .tabset-fade}
-----

```{r}
source("R Scripts/Snippets for Markdown/Common Openings.r")
source("R Scripts/Snippets for Markdown/Result Distribution.r")
```

### All Games

`r Master` playing with either White or Black pieces.

##### Most common openings played:

```{r}
tblOpenings

# Add a blank line after the list
  cat("\n\n")
```

##### Result Distribution:

```{r  fig.width=5, fig.height=4}
plotWinRate
```

### With White Pieces

`r Master` playing with White pieces.

##### Most common openings played:

```{r}
tblOpeningsWhite

# Add a blank line
  cat("\n\n")
  
```

##### Result Distribution:

```{r  fig.width=5, fig.height=4}
plotWinRateWhite
```

### With Black Pieces

`r Master` playing with Black pieces.

##### Most common openings played:

```{r}
tblOpeningsBlack

# Add a blank line after the list
  cat("\n\n")
```

##### Result Distribution:

```{r  fig.width=5, fig.height=4}
plotWinRateBlack
```

List of Games
=====

```{r, echo = FALSE, warning = FALSE}
source("R Scripts/Snippets for Markdown/Table of Master Games.r")

tblMasterGames
```
